---
title: "Hw_01_DataViz_R"
output: pdf_document
author: "Jessadakorn Vorathammaporn"
date: "2023-07-13"
---

## Install Library. \newline

```{r}
install.packages("tidyverse")
library(tidyverse) 
```
  
  
```{r}
install.packages("ggthemes")
library(ggthemes)
```
\newpage


## Chart 1 :

### What is the relationship between variable Price and Carrat ?  

### making a sample with 10 % of population. \newline

```{r}
set.seed(66)
small_diamonds <- sample_frac(diamonds, size = 0.1)
```

### Scatter plot of Price vs. Carat \newline

```{r}
ggplot(data = small_diamonds, mapping = aes(x = carat , y = price, col = price )) +
  geom_point(alpha = 0.8) +
  geom_smooth(col = "black", se = F) +
  theme_minimal() +
  scale_colour_gradient_tableau('Red') +
  labs(title = "Scatter plot of Price vs. Carat",
       subtitle =  "DataSet : Diamonds with random sample size = 10 %",
       x = "Carat",
       y = "Price")
```

> The relation between Price and Carrat are **Possitive**,
> meaning that if the value of the Carrat increase the Price of the diamond also increase \newline


## Chart 2 : \newline

### What is the distribution of price look like ? \newline

### Histogram of variable Price \newline

```{r}
ggplot(diamonds, mapping = aes(x = price)) +
  geom_histogram(bins = 100, fill = "#5c8991") +
  theme_minimal() +
  labs(title = "The Distribution of Price",
       subtitle = "Dataset : Diamond",
       x = "Price",
       y = "Count")
```

\newpage

### Density plot of variable Price \newline


```{r}

ggplot(diamonds, mapping = aes(x = price)) +
  geom_density() +
  theme_minimal() +
  labs(title = "Density plot of Price",
       subtitle = "Dataset : Diamond",
       x = "Price",
       y = "Density")

```



> According to the Graphs, The Distribution of Price is **Right-Skewed**  Distribution with mean, median, mode and standart diviation :\newline

\newpage
### - Mean Value :\newline

```{r}
mean(diamonds$price, na.rm = TRUE)

```

### - Median Value :\newline


```{r}
median(diamonds$price, na.rm = TRUE)

```

### - Mode Value :\newline

```{r}
diamonds %>%
  count(price) %>%
  arrange(-n) %>%
  head(1)
```

### - Standard Deviation :\newline

```{r}
sd(diamonds$price)
```

\newpage

## Chart 3 : \newline
### Let's explor about clarity of diamond \newline
### - Bar graph of Clarity \newline


```{r}
ggplot(diamonds, aes(clarity)) +
  geom_bar(fill = "#5c8991") +
  theme_minimal() +
  labs(title = "Bar plot of Clearity",
       subtitle =  "DataSet : Diamonds")
```


> From above, SI1 is the top in therm of quantity following by VS2\newline

\newpage

## - Bar graph of Clarity vs. Cut \newline

```{r}
ggplot(diamonds, aes(clarity, fill = cut)) +
  geom_bar(position = "dodge") +
  theme_minimal() +
  coord_flip() +
  labs(title = "Bar plot of Clearity vs. Cut",
       subtitle =  "DataSet : Diamonds")
```

> From above showing that VS2 has hightest quantity of ldeal cut
\newpage

## Chart 4 : \newline
### Explor more about price and clarity\newline
### - The Boxplot of Price vs Clearity\newline

```{r}
ggplot(diamonds, aes(clarity, price)) +
  geom_boxplot() +
  theme_minimal() +
  labs(title = "Boxplot of Price vs. Clarity",
       subtitle =  "DataSet : Diamonds")
```

> According to the Boxplot, every type of clearity has outlier\newline

\newpage

## Chart 5 : \newline
### Explor more about relationship between Price and Carrat\newline
### - Scatter plot of Price and Clearity Segmented by Clearity\newline

```{r}
ggplot(small_diamonds, aes(carat, price, col = price)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method ="lm", col = "black") +
  scale_color_gradient(low = "#93d48c",high = "#3d593a") +
  facet_wrap(~clarity) +
  theme_minimal() +
  labs(title = "Scatter plot Price vs. Carrat by clarity",
       subtitle = "DataSet : Diamonds")
```

> Every type of clarity has positive relationship with Price\newline

\newpage

## - Scatter plot of Price and Clearity Segmented by Color \newline

```{r}
ggplot(small_diamonds, aes(carat, price, col = color)) +
  geom_point(alpha = 1) +
  scale_color_brewer(type = "div", palette = 6) +
  labs(title = "Scatter plot Price vs. Carrat by color",
       subtitle = "DataSet : Diamonds")
```

> the type of Color and Price has significant pattern\newline

