---
title: "Titanic"
author: "Jessadakorn Vorathammaporn"
date: "2023-07-19"
output: pdf_document
---

## Install Packages \newline

```{r}
install.packages("tidyverse")
install.packages("ggthemes")
install.packages("patchwork")
install.packages("titanic")
install.packages("caret")

library(tidyverse)
library(ggthemes)
library(patchwork)
library(titanic)
library(caret)
```
\newpage

## Load Data Set and Quick Explore the Data \newline

```{r}
df <- titanic_train
glimpse(df)
summary(df)
```

## Clean Data \newline
### Drop NA Values \newline

```{r}
df <- na.omit(titanic_train)
```

### Change columns : Survived, Pclass, Sex, Embarked to factor \newline

```{r}

df$Survived<- factor(df$Survived, level = c(0, 1), labels = c("not_survive", "survive"))
df$Pclass <- factor(df$Pclass, level = c(1,2,3), labels = c("1st", "2nd", "3rd"))
df$Sex <- factor(df$Sex, level = c("male", "female"))
df$Embarked <- factor(df$Embarked, level = c("C", "Q", "S"))

```

\newpage

## Exploratory Data Analysis \newline
### Let's Explore about Age \newline

```{r}

ggplot(df , aes(Age)) +
  geom_histogram(bins = 50, fill = "#b85849") +
  theme_minimal() +
  labs(title = "Histogram of Passenger Age in titanic")

```

```{r}
ggplot(df , aes(Age)) +
  geom_density()
```

> The Distribution of Age are **Right-Skew Distribution** with Mean, Median, SD, Min, Max \newline

```{r}
df %>%
  select(Age) %>%
  summarise(mean_age = mean(Age), med_age = median(Age), sd_age = sd(Age), 
            min_age = min(Age), max_age = max(Age))
```

### Top 5 Age of Passenger \newline

```{r}
df %>%
  count(Age) %>%
  arrange(-n) %>%
  head(5)
```

### Let's Explore about Passenger Class \newline

```{r}
ggplot(df, aes(Pclass, fill = Survived)) +
  geom_bar(position =  "dodge") +
  theme_minimal() +
  labs(title = "Passenger Class vs Surviving",
       x = "Passenger Class")
```

> Most of passenger that not survive are **3rd Class passenger**.
> Meanwhile, survied passenger mostly are  **1st Class passenger** \newline

\newpage

### Let's Explore about gender \newline

```{r}
ggplot(df, aes(Sex, fill = Survived)) + 
  geom_bar(position = "dodge") +
  theme_minimal() +
  labs(title = "Gender vs. Surviving",
       x = "Gender")
```

> Survived Passengers mostly are **Female** \newline

\newpage

### Let's Explore about Siblings/Spouses Aboard and Parch \newline

```{r}
df %>%
  select(SibSp, Survived) %>%
  count(SibSp, Survived)

df %>%
  select(Parch, Survived) %>%
  count(Parch, Survived)
```

\newpage

## Training Model \newline
### Setting up
### Split the data set to : 
### 70% Train data and 30% Test data \newline

```{r}

set.seed(42)
n <- nrow(df)
id <- sample(1:n, size = 0.7 * n)
train_data <- df[id,]
test_data <- df[-id,]

```

## Creating Confusion Matrix Calculator \newline
```{r}

confusion_matrix_cal <- function(predicted, actual) {
  
  con_m <- table(predicted, actual, dnn = c("Predicted", "Actucal"))
  print(con_m)
  
  acc <- (con_m[1,1] + con_m[2, 2]) / sum(con_m)
  cat("Accuracy :", acc) 
  
  pre <- con_m[2,2] / (con_m[2,1] + con_m[2,2])
  cat("\nPresision :", pre)
  
  rec <- con_m[2,2] / (con_m[1,2] + con_m[2,2])
  cat("\nRecall :", rec)
  
  f1 <- (2*pre*acc) / (pre + acc)
  cat("\nF1 :", f1)
}

```

\newpage


## Using Logistic Regression with \newline 
### Dependent Variable : Survived 
### Independent Variabel : Passenger Class, Gender, Age, Number of Siblings, Number of Parents \newline 

```{r}
model <- glm(Survived ~  Pclass + Sex + Age + SibSp + Parch  , data = train_data, family = "binomial")
summary(model)
```

\newpage

## Testing model with Training data 
### By using 0.60 probability to cut off \newline

```{r}
train_data$prob_sur <- predict(model, type = "response")
train_data$pred_sur <- ifelse(train_data$prob_sur >= 0.6, "survive", "not_survive" )
con_m1 <- confusion_matrix_cal(train_data$pred_sur, train_data$Survived)
```

## Testing model with unseen data
### By using 0.60 probability to cut off \newline
```{r}
test_data$prob_sur <- predict(model, newdata = test_data)
test_data$pred_sur <- ifelse(test_data$prob_sur >= 0.6, "survive", "not_survive" )
con_m2 <- confusion_matrix_cal(test_data$pred_sur, test_data$Survived)
```



